A bicolor nested sequents for intuitionistic modal logics

### 2020-05-11 bicolor NS/abstract/wil20.tex
adding definition

\begin{equation*}
\label{eq:ik}%\hskip-2em
\begin{array}[t]{r@{\;}l@{\qquad}r@{\;}l@{\qquad}r@{\;}l}
\kax[1]\colon&\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)
&
\kax[3]\colon&\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)
&
\kax[5]\colon&\DIA\BOT\IMP\BOT
\\
\kax[2]\colon&\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)
&
\kax[4]\colon&(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)\\%x[1ex]
\end{array}
\end{equation*}
%%
\section{Bicolor nested sequent system}

@@

>>>>

\begin{equation*}
\label{eq:ik}%\hskip-2em
\begin{array}[t]{r@{\;}l@{\qquad}r@{\;}l@{\qquad}r@{\;}l}
\kax[1]\colon&\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)
&
\kax[3]\colon&\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)
&
\kax[5]\colon&\DIA\BOT\IMP\BOT
\\
\kax[2]\colon&\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)
&
\kax[4]\colon&(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)\\%x[1ex]
\end{array}
\end{equation*}
%%
We recall the birelational models [21, 7] for intuitionistic modal logics, which are a combination of the Kripke semantics for propositional intuitionistic logic and the one for classical modal logic. A \emph{birelational frame} $\F = \langle W, R, \le \rangle$ is a non-empty set $W$ of worlds together with two binary relations $\le, \rel \subseteq W \times W$, where $\le$ is a preorder(i.e., reflexive and transitive), such that the following two conditions hold:

\begin{enumerate}
	\item[($\rn{F_1}$)] For $u, v, v' \in W$, if $u \rel v$ and $v \le v'$, there exists $u'$ s.t.~$u \le u'$ and $u' \rel v'$.

	\item[($\rn{F_2}$)] For $u', u, v \in W$, if $u \le v$, there exists $v'$ s.t.~$u' \rel v'$ and $v\le v'$.
\end{enumerate}

\section{Bicolor nested sequent system}

@@

\marianela{add F1 rule?}
